Supplementary information

### 2018-06-13 supplementary_information.Rmd
Minor fixes to comments and supplementary info

correlation_scatter_cap <- paste(
  "Pairwise mean squared trait correlation values as a function of sample size.",
  "Note that the x-axis uses a $\\log_10$ scale."
)
correlation_fig_cap <- paste(
  "Fraction of statistically significant ($p < 0.05$) pairwise trait correlation estimates",
  "as a function of sample size for each plant functional type."
)
```

>>>>

correlation_scatter_cap <- paste(
  "Pairwise mean squared trait correlation values as a function of sample size.",
  "Note that the x-axis uses a $\\log_{10}$ scale."
)
correlation_fig_cap <- paste(
  "Fraction of statistically significant ($p < 0.05$) pairwise trait correlation estimates",
  "as a function of sample size for each plant functional type."
)
```
